A general Nullstellensatz for generalized spaces

### 2019-03-17 paper-qcoh.tex
typo

\begin{proof}Injectivity is by the Nullstellensatz of
Theorem~\ref{thm:nullstellensatz}. Surjectivity is by the definability
result~\cite[Theorem~2.2]{caramello:definability}, exploiting that the internal
statement localizes well by Lemma~\ref{lemma:truth-to-provability}.
% XXX check reference number
\end{proof}

>>>>

\begin{proof}Injectivity is by the Nullstellensatz of
Theorem~\ref{thm:nullstellensatz}. Surjectivity is by the definability
result~\cite[Theorem~2.4]{caramello:definability}, exploiting that the internal
statement localizes well by Lemma~\ref{lemma:truth-to-provability}.
\end{proof}
